### 2014-03-31 tex/main-body-text.tex
minor edits during a brief read-through

Methods for the unsupervised clustering of genotypes have received 
considerable attention in the molecular ecology literature.  
The best known example of this class of methods is {\sc structure} 
\citep{Pritchardetal2000}.  {\sc structure} itself can be interpreted 
as an elaboration of earlier models used to identify the spawning 
stock of salmon \citep{Smouseetal1990}, and a variety of other 
clustering methods have been developed that are all closely related to 
{\sc structure}, for example {\sc NewHybrids} \citep{And&Tho2002}, {\sc 
BayesAss+} \citep{Wil&Ran2003}, and {\sc baps} 
\citep{Coranderetal2004}. (An overview of these similarities can be 
found in \citealt{Anderson2009PGAC}.)

@@

Here, we provide a different perspective on the {\sc flock} algorithm
showing it to be a special, restricted case of the simulated annealing algorithm for finding the Bayesian maximum {\em a posteriori} (MAP) estimate from a marginalized form of the {\sc structure} model with no admixture and non-correlated allele frequencies.

\section*{Comparison of methods}
We start with a succinct mathematical description of the {\sc flock} algorithm, and then\ldots

>>>>

Methods for the unsupervised clustering of genotypes have received 
considerable attention in the molecular ecology literature.  
The best known example of this class of methods is {\sc structure} 
\citep{Pritchardetal2000}.  {\sc structure} itself can be described 
as an elaboration of earlier models used to identify the spawning 
stock of salmon \citep{Smouseetal1990}, and a variety of other 
clustering methods have been developed that are all closely related to 
{\sc structure}, for example {\sc NewHybrids} \citep{And&Tho2002}, {\sc 
BayesAss+} \citep{Wil&Ran2003}, and {\sc baps} 
\citep{Coranderetal2004}. An overview of these similarities can be 
found in \citet{Anderson2009PGAC}.

@@

Here, we provide a different perspective on the {\sc flock} algorithm,
showing it to be a special, restricted case of the simulated annealing algorithm for finding the Bayesian maximum {\em a posteriori} (MAP) estimate from a marginalized form of the {\sc structure} model with no admixture and non-correlated allele frequencies.

\section*{Comparison of methods}
We start with a succinct mathematical description of the {\sc structure} algorithm, and then\ldots
